Representations for Printing\\ \Large Natural Language Processing Toolkit: Technical Report

### 2001-12-07 technical/printing/printing.tex
Added copyright/license notices to all files
svn/trunk@82
- Revised design goals - Added section discussing str vs repr, etc. - Added a list of guidelines (incomplete)
svn/trunk@403

%
% Natural Language Toolkit for Python
% Representations for Printing
% Edward Loper
% 
% Created [05/27/01 11:44 PM]
% $Id$
%

@@

@@

@@

@@

%============= PRINTING REPS =============%
\section{Printing Representations}

Here's a list of how I'm currently representing things:

\newpage
\begin{tabbing}
\tt
\hspace{3in}\=\\
\textbf{$>>>$ print Location(1, 3)}\\
@[1:3]\\
\textbf{$>>>$ print Location(1, 2)}\\
@[1]\\
\textbf{$>>>$ print Location(1, 3, source='foo.txt')}\\
@[1:3]@'foo.txt'\\
\textbf{$>>>$ print Location(1, 3, unit='word')}\\
@[word 1:word 3]\\
\textbf{$>>>$ print Location(1, 2, unit='word', source='foo.txt')}\\
@[word 1:word 2]\\
\\
\textbf{$>>>$ print Token('hi', Location(1, 2))}\\
'hi'@[1]\\\
\textbf{$>>>$ print Token('hi', Location(1, 3))}\\
'hi'@[1:3]\\\
\textbf{$>>>$ print Token('hi', Location(1, 3, unit='word', source='foo.txt'))}\\
'hi'@[1:3] \>\textrm{Loc's unit and source are not shown}\\
\textbf{$>>>$ }\\
\\
\textbf{$>>>$ print Tree('np', 'the', 'boy')}\\
('np': 'the' 'boy') \>\textrm{No commas and presence of ':' distinguises from tuple}\\
\textbf{$>>>$ print Tree('vp', 'likes', Tree('np', 'the', 'boy'))}\\
('vp': 'likes' ('np': 'the' 'boy'))\\
\textbf{$>>>$ print TreeToken('vp', Token('likes',1), Tree('np', Token('John',2)))}\\
('vp': 'likes' ('np': 'John))@[1:3]\\

\end{tabbing}

>>>>

% Natural Language Toolkit Technical Report:
% Representations for Printing
%
% Copyright (C) 2001 University of Pennsylvania
% Author: Edward Loper <edloper@gradient.cis.upenn.edu>
% URL: <http://nltk.sf.net>
% For license information, see LICENSE.TXT
%
% $Id$

@@

  \subsection{Primary Goals}

@@

  \subsection{Secondary Goals}

@@

%============= PYTHON =============%
\section{Python Constructs}

  Python classes may define two different string representations: one
  is returned by \texttt{str}, and the other by \texttt{repr}.  The
  differences between these two represenetations are:

    \item The ``Official'' Definitions
    (\texttt{http://www.python.org/doc/current/ref/customization.html})
    \begin{itemize}
      \item 
        \texttt{repr}: If at all possible, this should look like a
        valid Python expression that could be used to recreate an
        object with the same value (given an appropriate
        environment). If this is not possible, a string of the form
        "$<$...some useful description...$>$" should be returned.
        This is typically used for debugging, so it is important that
        the representation is information-rich and unambiguous.

      \item
        \texttt{str}: This differs from \_\_repr\_\_() in that it does not
        have to be a valid Python expression: a more convenient or
        concise representation may be used instead. 
    \end{itemize}

    \item Usage Contexts
    \begin{itemize}

      \item \texttt{repr}
      \begin{itemize}
        \item The result of \texttt{repr()}
        \item The result of backquotes (e.g., \texttt{`x`})
        \item The result of the string formatting operator
            ``\texttt{\%r}''
        \item Used when an object representation is ``contained'' in
            another object representation (e.g., to display an element
            of a list or a key of a dictionary)
      \end{itemize}

      \item \texttt{str}
      \begin{itemize}
        \item The result of \texttt{str()}
        \item The result of the string formatting operator 
            ``\texttt{\%s}''
        \item The output of print
      \end{itemize}

    \item Builtin Type Usage Conventions
    \begin{itemize}
      \item \texttt{repr(x)} contains no newlines.
      \item \texttt{repr(x)} contains only simple ASCII characters.
    \end{itemize}

    \item Default Values
    \begin{itemize}
      \item The default value for \texttt{repr} is a string of the form:\\
        \texttt{$<$\_\_\textit{module}\_\_.\textit{class} instance at \textit{address}$>$}
      \item The default value for \texttt{str} is the value returned
        by \texttt{repr}
    \end{itemize}

  \subsection{The Official Definition}

    After consideration of the contexts in which \texttt{repr} and
    \texttt{str} are used, we have decided \emph{not} to make use of
    the ``official'' definitions.  This decision is primarily
    motivated by the fact that \texttt{repr} is always used when an
    object representation is ``contained'' in another object
    representation.  We believe that this would lead to overly verbose
    and difficult to read representations of complex objects.  For
    example, if we adopted the ``official'' definition of
    \texttt{repr}, then the string representation (using \texttt{repr}
    \emph{or} \texttt{str}) of a list of tokens would look something
    like:

\begin{verbatim}
"[Token('The', Location(0, 1, unit='w', source='foo.txt')), Token('dog', Lo
cation(1, 2, unit='w', source='foo.txt')), Token('saw', Location(2, 3, unit
='w', source='foo.txt')), Token('the', Location(3, 4, unit='w', source='foo
.txt')), Token('man', Location(4, 5, unit='w', source='foo.txt'))]"
\end{verbatim}

    We believe that this is signifigantly less readable than the
    result of using a \texttt{repr} which does not evaluate to return
    its original value:

\begin{verbatim}
"['The'@[0w]@'foo.txt', 'dog'@[1w]@'foo.txt', 'saw'@[2w]@'foo.txt', 'the'@[
3w]@'foo.txt', 'man'@[4w]@'foo.txt']"
\end{verbatim}

  \subsection{str vs repr}

    Instead, we will make the following distinction between the
    \texttt{str} and \texttt{repr} string representations:

      \item \texttt{repr} gives a single-line representation, which
          would be suitable for inclusion in the representation of
          another object (i.e., it is delimited by quotes, brackets,
          braces, etc., when appropriate).  This representation should
          contain only standard ASCII characters.  \texttt{repr}
          should be defined for all classes.

      \item \texttt{str} can optionally give a more human-readable
          representation of an object.  This representation may span
          multiple lines.
    \end{itemize}

\section{Guidelines}

  The following guidelines are intended to help design string
  representations for new nltk objects.  In these guidelines, the
  string representation of an object is refered to as \texttt{s}.

  \subsection{General Guidelines}
    \begin{itemize}
      \item All classes should implement \texttt{repr}.  When the
        output of \texttt{repr} may be difficult to read, \texttt{str}
        should be implemented.
      \item If a field has no value (or the default value), it may be
        ommited from the printed representation.  (E.g.,
        \texttt{Location}s with no source don't display the source.
      \item When \texttt{s} needs to contain the representation of an
        embedded object, and the object's type is variable,
        \texttt{repr} should always be used (not \texttt{str}).  No
        special type-checking should be applied (e.g., to treat
        strings specially).
      \item It should always be possible to tell the type of an object
          from its printed representation.
    \end{itemize}

  \subsection{Repr}
    \begin{itemize}
      \item \texttt{s} may not span multiple lines (i.e., it may not
        contain newlines)
    \end{itemize}

  \subsection{Str}
    \begin{itemize}
      \item \texttt{s} may span multiple lines.
      \item Multiline \texttt{str} representations shoud not contain any
        trailing newlines.
      \item \texttt{s} may use indentation to show internal structure.
      \item \texttt{s} may be a simple table.
      \item If \texttt{s} is a multiline representation, it should try 
        very hard not to be more than 75 characters wide.
      \item It should always be possible to distinguish the
          \texttt{s} from the \texttt{str} for any built-in object
          (except strings, which can have arbitrary representations);
          or for any other class.
      \item For multiline \texttt{str} representations, \texttt{s}
        should begin with an unindented line, whose first word is the
        name of the class.  All subsequent lines should be indented.
    \end{itemize}

  \subsection{Data-Oriented Classes}
    \begin{itemize}
      \item When practical, \texttt{s} should specify the complete
          state of the object.  In particular, if it is possible to
          give the complete state of a typical instance in less than
          75 characters, then \texttt{s} should give the complete
          state.  
      \item When it is not practical to show the complete state
          of a data-oriented instance, this should be indicated with
          elipsis dots (``...'').
    \end{itemize}

  \subsection{Task-Oriented Classes}
    \begin{itemize}
      \item For repr, \texttt{s} should have the form:\\
        \texttt{$<$\textit{class} \textit{info}$>$}\\
        where \texttt{\textit{info}} is a description of the
        parameters and the state of the class.
    \end{itemize}

%============= PP =============%
\section{Pretty-Printing Methods}

  Classes may provide pretty-printing methods.  These methods should
  have the following signature:

  \texttt{pp(self, left, right)}

  Where \texttt{left} and \texttt{right} are left and right margins.
  \texttt{pp} should assume that it is already at position
  \texttt{left}.  E.g., a pp function to draw a vertical line, when
  given \texttt{left}=5, would return:

  \texttt{"|" + ("~~~~~|"*lineheight)}

%============= EXAMPLES =============%
\section{Examples}

\subsection{Locations}

  \texttt{str} and \texttt{repr} representations are identical.  Unit
  \& Loc are not displayed if they are not specified.  End index is not
  displayed if it has the default value (=start+1).

{\tt
\begin{tabbing}
\emph{$>>>$ Location(1, 3)}\\
@[1:3]\\
\emph{$>>>$ Location(1, 2)}\\
@[1]\\
\emph{$>>>$ Location(1, 3, source='foo.txt')}\\
@[1:3]@'foo.txt'\\
\emph{$>>>$ Location(1, 3, unit='w')}\\
@[1w:3w]\\
\emph{$>>>$ Location(1, 2, unit='w', source='foo.txt')}\\
@[1w]@'foo.txt'\\
\emph{$>>>$ Location(1, 3, unit='w', source='foo.txt')}\\
@[1w:3w]@'foo.txt'
\end{tabbing}
}

\subsection{Tokens}

  \texttt{str} and \texttt{repr} representations are identical.
  Location is included using \texttt{repr}.  If location is
  unspecified, it is displayed as \texttt{@[?]}.  (Note that this
  would never be a valid location by itself.)

{\tt
\begin{tabbing}
\emph{$>>>$ Token('x', Location(1, 3, unit='w', source='foo.txt')}\\
'x'@[1w:3w]@'foo.txt'\\
\emph{$>>>$ Token('x')}\\
'x'@[?]
\end{tabbing}
}

\subsection{Trees}

  Lack of commas, and presence of ':', distinguises trees from tuples.

{\tt
\begin{tabbing}
\emph{$>>>$ Tree('np', 'the', 'boy')}\\
('np': 'the' 'boy') \\
\emph{$>>>$ Tree('vp', 'likes', Tree('np', 'the', 'boy'))}\\
('vp': 'likes' ('np': 'the' 'boy'))\\
\emph{$>>>$ TreeToken('vp', Token('likes',1), TreeToken('np', Token('John',2)))}\\
('vp': 'likes' ('np': 'John))@[1:3]\\
\\
\textrm{Trees have one-line repr representations, \& multiline str representations:}\\
\emph{$>>>$ Tree('x', 'a'*40, Tree('b', 'c'*40, Tree('d', 'e'*40)))}\\
('x': 'aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa' ('b': 'cccccccccccccccccccccccc\\
cccccccccccccccc' ('d': 'eeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeee')))\\
\emph{$>>>$ print Tree('x', 'a'*40, Tree('b', 'c'*40, Tree('d', 'e'*40)))}\\
('x':\\
\qquad  'aaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaaa'\\
\qquad  ('b':\\
\qquad\qquad    'cccccccccccccccccccccccccccccccccccccccc'\\
\qquad\qquad    ('d': 'eeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeeee')))
\end{tabbing}
}

\subsection{SimpleFreqDists}

{\tt
\begin{tabbing}
\emph{$>>>$ s = SimpleFreqDist(\ldots)}\\
\{SimpleFreqDist $<$CFSample 1, '7'$>$:1, $<$CFSample 5, '2'$>$:1, $<$CFSample 3, '2'$>$\\
:1, $<$CFSample 2, '7'$>$:1, $<$CFSample 7, '2'$>$:2, $<$CFSample 9, '7'$>$:2, $<$CFSampl\\
e 6, '7'$>$:3, $<$CFSample 5, '7'$>$:1, $<$CFSample 3, '7'$>$:1, $<$CFSample 9, '9'$>$:2,\\
 $<$CFSample 7, '9'$>$:3, $<$CFSample 8, '5'$>$:5\}\\
\emph{$>>>$ print s}\\
\{SimpleFreqDist\\
\qquad $<$CFSample 1, '7'$>$: 1, $<$CFSample 5, '2'$>$: 1, $<$CFSample 3, '2'$>$: 1, \\
\qquad $<$CFSample 2, '7'$>$: 1, $<$CFSample 7, '2'$>$: 2, $<$CFSample 9, '7'$>$: 2, \\
\qquad $<$CFSample 6, '7'$>$: 3, $<$CFSample 5, '7'$>$: 1, $<$CFSample 3, '7'$>$: 1, \\
\qquad $<$CFSample 9, '9'$>$: 2, $<$CFSample 7, '9'$>$: 3, $<$CFSample 8, '5'$>$: 5\}
\end{tabbing}
}

@@
